\SW: II. New Gravitational Lens Candidates from the CFHTLS Discovered through Citizen Science

### 2015-05-08 doc/sw-cfhtls.tex
Reworded abstract

\begin{abstract}
We report the discovery of {\bf 29 promising (and 59 total)} new lens
candidates from the CFHT Legacy Survey (\cfhtls) based on about 11
million classifications performed by citizen scientists as part of the
first \sw lens search.  The goal of the blind lens search was to
identify lenses missed by lens finding robots (the \rf on galaxy scales
and \af on group/cluster scales), which have been previously used to
mine the \cfhtls for lenses.  We compare some properties of lens samples
detected by these algorithms to the \sw sample and found that they are
broadly similar.  The image separation distribution calculated from the
\sw discovered sample shows that our previous constraints on the average
density profile of the lenses are robust. \sw recovers about
60~per~cent of the known sample and the new candidates show a richer variety
compared to the lenses found by the two robots. We find that analyzing
only those classifications which are performed by high power
volunteers, \sw can achieve a detection rate of up to 75~per~cent for the known
lens sample.  Training and calibration of the performance of citizen
scientists is crucial for the success of \sw. We also present the SIMCT
pipeline, used for generating a sample of realistic simulated lensed
images in the \cfhtls, and samples of duds and false positives used in
the training.  Such a training sample has a legacy value for testing
future lens finding algorithms. We make our training sample publicly
available.

>>>>

\begin{abstract}
We report the discovery of {\bf 29 promising (and 59 total)} new lens
candidates from the CFHT Legacy Survey (\cfhtls) based on about 11
million classifications performed by citizen scientists as part of the
first \sw lens search.  The goal of the blind lens search was to
identify lens candidates missed by robots (the \rf on galaxy scales
and \af on group/cluster scales) which had been previously used to
mine the \cfhtls for lenses.  We compare some properties of the samples
detected by these algorithms to the \sw sample and find them to be
broadly similar.  The image separation distribution calculated from the
\sw sample shows that previous constraints on the average
density profile of lens galaxies are robust. \sw recovers about
60\% of known lenses, while the new candidates show a richer variety
compared to those found by the two robots. This detection rate could be
increased to 75\% by only using classifications performed by expert
volunteers (albeit at the cost of a higher false positive rate), indicating that
the training and performance calibration of the citizen
scientists is very important for the success of \sw. In this work
we present the SIMCT pipeline, used for generating {\it in situ}
a sample of realistic  simulated lensed
images.  This training sample, along with the
false positives identified during the
search, has a legacy value for testing
future lens finding algorithms. We make this dataset publicly
available.
